### 2014-12-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012 Report: Introductory material and instrumentation descriptions

@@

@@

@@

@@

>>>>

NIST FFTG

Objective: To improve the safety and effectiveness of firefighters through measurement science to advance suppression tactics, examine non-traditional means of fire suppression, and transfer of the results to the fire service.

Aid the fire service across the country in the most effective and safe way to fight fires.

The goal is to improve the safety of not only the responding firefighters but the public as well through the use of modern fire suppression tactics for modern fires.

Approach: Real scale, instrumented fire suppression experiments.

This is an STRS project that has been complemented with OA studies funding from: 
Cal Poly 
FDNY 
ISFSI 
NYU

NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.  The studies have resulted in guidance to the fire service regarding ventilation tactics.  However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.

Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice.  This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.

Test Objectives:

1)	Examine the water distribution for solid streams, straight streams, and fog streams.

2)	Examine the impact of solid streams, straight streams, and fog streams on the cooling of fire gases inside a structure with various flow path configurations, structure configurations, and structure volumes.

Constants: 
Building Geometry
Fuel Load
Fire Room Conditions at time of water flow
Water Flow Rate – 120 gpm

Variable: 
Smooth Bore vs Narrow Fog

@@

WATER DISTRIBUTION

Purpose:
- Determine the appropriate location for nozzles
- Determine water distribution

Setup:
Task Force Tips Metro 1, Fixed Gallonage (120 gpm)
Straight Stream
30 degree Fog
7/8” Smooth Bore
100 ft of 1-3/4 inch hose

The hose streams were from fixed monitor nozzles simulating a firefighter with the hose line in the structure.

Controlled and operated via a gate valve from the exterior.

12 Experiments:
4 SS from room
2 Fog from room
2 SS from Hall
2 Fog from Hall
1 SB from Hall
1 SB from Room

2.5 square foot collector bin.

Bins were poly boxes with interlacing lips to prevent water from going in between.

Measured how much of the water ended up in what part of the room.

The building was sheathed in plastic for the water flow tests as to protect and preserve the structure before any fire suppression tests were conducted.

Spray Distribution Summary:
- Experiments provided nozzle placement for gas cooling and fire suppression experiments.
- Provide a sense of the distribution of the water throughout the test space.

Hallway nozzle = gas cooling

Room nozzle = seat of fire

FIRE SUPPRESSION

Room and contents fire inside structure
Two points of interior attack
- Remotely activated in hallway (indirect attack)
- Remotely activated in fire room (direct attack)

Common household furnishings.

Due to the limited time and resources for testing, the extremes were chosen: smooth bore and narrow fog.

Straight stream from a fog nozzle was the medium between the two.

@@

Thermocouples:
Work through the Seebeck effect.  Two dissimilar metals are joined together with a weld bead.  Each metal generates a voltage, different from one another, when exposed to a thermal gradient.  This voltage difference increases with an increase in energy to the thermocouple and through a correlation, a corresponding temperature is found.

@@

Total Heat Flux:
Water cooled heat flux gauges measure both the convective and radiative heat transfer to the sensor.  Hot and cold side of a plate simulating the hot and cold side of a thermocouple.  The temperature gradient generates a voltage and through correlations, a total heat flux measurement is obtained.  The sensor is water cooled to ensure a thermal gradient remains and the sensor does not reach uniform temperature.  The sensor top is painted black to assist with radiation absorption.

Radiometer:
The radiometer is simply a total heat flux gauge with Zirconium plate atop the sensor preventing the device from recording any heat due to convective transfer.

@@

Bi-directional Probes:
- Fire flow measurements are taken using these devices which have a high and low pressure side.  These flows then travel to a pressure transducer.  Through a simple conversion, the voltages are converted to pressure and finally a velocity based on the pressure and corresponding temperature measurements.
